An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-04-29 CMPSpaper_writing/CMPSpaper_writing.Rmd
found the place to substitute the ```{=latex}
add other codefig plots

```{r, echo=FALSE}
library(knitr)

@@

codefigChunkHook <- function(x, options) {
  main <-  defaultChunkHook(x, options)
  before <-
    "\\vspace{1em}
\\begin{adjustbox}{valign=t}
\\begin{minipage}{.49\\textwidth}\n"
  after <-
    paste("\\vspace{1em}
\\end{minipage}
\\begin{minipage}{.49\\textwidth}",
    paste0("\\includegraphics[width=\\textwidth]{CMPSpaper_writing_files/figure-latex/",
                 options[["label"]], "-1.pdf}
\\end{minipage}
\\end{adjustbox}"),
          sep = "\n")
  ## Was a codefig option supplied in chunk header?
  ## If so, wrap code block and graphical output with needed LaTeX code.
  if (!is.null(options$codefig)) {
    return(sprintf("%s%s\n%s", before, main, after))
  } else {
    return(main)
  }
}

@@

```{r eval=FALSE}
dframe %>% 
  ggplot(aes(x = land1, y = land2, fill = CMPS.score)) +
    geom_tile() +
    scale_fill_gradient2(low="darkgrey", high = "darkorange", mid=6) +
    geom_text(aes(label=CMPS.score))

```

@@

<!--
```{r, eval=FALSE}
sig.plot$signature_shift_plot
```
-->

@@

As `cmps_signature_plot` focuses on the signature level, on the other hand, `cmps_segment_plot` focuses on the segment level. It not only takes the "full result" of `extract_feature_cmps`, but also takes an argument `seg.idx`, which indicates which segment to be inspected. For example, after checking `sig.plot$seg.pos` we noticed that segment 6 is not one of the congruent matching profile segments. So we can set `seg.idx = 6` in order to have a closer look at segment 6 and why it disagrees with the congruent registration position. `cmps_signature_plot` also returns a list. Each element of this list is also a list and corresponds to one segment scale of this basis segment.

```{r, eval=FALSE}
seg.plot <- cmps_segment_plot(cmps_with_multi_scale, seg.idx = 6)
```

@@

```{r, eval=FALSE}
seg.plot[[1]]$segment_plot
```

```{r, echo=FALSE, eval=FALSE, out.width="300px", fig.cap="segment\\_plot for segment 6 at scale 1. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments. "}
knitr::include_graphics("img/segplot1.png", dpi = 100)
```

@@

```{r, eval=FALSE}
seg.plot[[1]]$scale_ccf_plot
```

```{r, echo=FALSE, out.width="300px", fig.cap="scale\\_ccf\\_plot shows the cross-correlation curve between the comparison signature and segment 6 at scale 1. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a candidate position for the consistent correlation peak; the blue dashed lines show the region of the tolerance zone. We can see here none of the five highest peaks agrees with the candidate position, so a consistent correlation peak cannot be identified and we don't take segment 6 as a congruent matching profile segment"}
knitr::include_graphics("img/segplot2.png", dpi = 100)
```

@@

```{r, eval=FALSE}
library(ggpubr)

ggarrange(plotlist = unlist(seg.plot, recursive = FALSE),
          ncol = 2, nrow = 3)
```

```{r, echo=FALSE, out.width="400px", fig.cap="put segment\\_plot and scale\\_ccf\\_plot of all scales together. We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1). Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment. Here we can also see clearly that increasing segment length can reduce the number of false positive peaks."}
knitr::include_graphics("img/segplot3.png", dpi = 100)
```

>>>>

```{r, echo=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(bulletxtrctr)

@@

codefigChunkHook <- function(x, options) {
  main <-  defaultChunkHook(x, options)
  before <-
    "\\vspace{1em}
\\begin{adjustbox}{valign=t}
\\begin{minipage}{.49\\textwidth}\n"
  after <-
    paste("\\vspace{1em}
\\end{minipage}
\\begin{minipage}{.49\\textwidth}",
    paste0("\\includegraphics[width=\\textwidth]{CMPSpaper_writing_files/figure-latex/",
                 options[["label"]], "-1.pdf}
\\end{minipage}
\\end{adjustbox}"),
          sep = "\n")
  ## Was a codefig option supplied in chunk header?
  ## If so, wrap code block and graphical output with needed LaTeX code.
  if (!is.null(options$codefig)) {
    main <- gsub("```","", main)
    main <- gsub("=latex","", main)
    return(sprintf("%s\n%s\n%s", before, main, after))
  } else {
    return(main)
  }
}

@@

```{r eval=TRUE, echo=FALSE}

lands <- unique(bullets$bulletland)

comparisons <- data.frame(expand.grid(land1 = lands[1:6], land2 = lands[7:12]), 
                          stringsAsFactors = FALSE)

comparisons <- comparisons %>% mutate(
  aligned = purrr::map2(.x = land1, .y = land2, 
                        .f = function(xx, yy) {
                          land1 <- bullets$sigs[bullets$bulletland == xx][[1]]
                          land2 <- bullets$sigs[bullets$bulletland == yy][[1]]
                          land1$bullet <- "first-land"
                          land2$bullet <- "second-land"

                          sig_align(land1$sig, land2$sig)
                        }))

comparisons <- comparisons %>% 
  mutate(cmps = aligned %>% purrr::map(.f = function(a) {
    extract_feature_cmps(a$lands$sig1, a$lands$sig2, include = "full")
  }))

comparisons <- comparisons %>% 
  mutate(
    cmps_score = sapply(comparisons$cmps, function(x) x$CMPS.score),
    cmps_nseg = sapply(comparisons$cmps, function(x) x$nseg)
  )

# dframe <- comparisons %>% select(land1, land2, cmps_score)
# 
# dframe %>% 
#   ggplot(aes(x = land1, y = land2, fill = cmps_score)) +
#   geom_tile() +
#   scale_fill_gradientn(
#     colors=c("darkgrey","darkorange")
#   ) +
#   geom_text(aes(label=cmps_score)) +
#   theme_bw() + 
#   coord_flip()

comparisons <- comparisons %>%
  mutate(
    bulletA = gsub("(\\d)-\\d", "\\1", land1),
    landA = gsub("\\d-(\\d)", "\\1", land1),
    bulletB = gsub("(\\d)-\\d", "\\1", land2),
    landB = gsub("\\d-(\\d)", "\\1", land2)
  )

# comparisons %>%   
#   group_by(bulletA, bulletB) %>% tidyr::nest() %>%
#   mutate(
#     cmps_max_bar = data %>% purrr::map_dbl(
#       .f = function(d) max(compute_average_scores(land1 = d$landA,
#                                                   land2 = d$landB,
#                                                   d$cmps_score)))
#   )

dframe <- comparisons %>% select(-aligned, -cmps)
```

```{r, echo=FALSE}
dframe %>% ggplot(aes(x = landB, y = landA, fill = cmps_score)) + geom_tile() + 
  scale_fill_gradient2(low = "gray80", high = "darkorange", midpoint = 6) + 
  facet_grid(bulletA ~ bulletB, labeller = "label_both") + xlab("Land B") + 
  ylab("Land A") + theme(aspect.ratio = 1) +
  geom_text(aes(label=cmps_score)) +
  theme_bw()
```

<!-- ```{r} -->
<!-- #      [,1] [,2] [,3] [,4] [,5] [,6] -->
<!-- # [1,]    2    3    2    3    1    2 -->
<!-- # [2,]    2    1   17    1    2    3 -->
<!-- # [3,]    1    1    3   14    2    2 -->
<!-- # [4,]    2    1    1    1   10    1 -->
<!-- # [5,]    2    2    1    1    1   15 -->
<!-- # [6,]   16    3    1    2    1    1 -->
<!-- ``` -->

@@

@@

As `cmps_signature_plot` focuses on the signature level, on the other hand, `cmps_segment_plot` focuses on the segment level. It not only takes the "full result" of `extract_feature_cmps`, but also takes an argument `seg.idx`, which indicates which segment to be inspected. For example, after checking `sig.plot$seg_shift` we noticed that segment 6 is not one of the congruent matching profile segments. So we can set `seg.idx = 6` in order to have a closer look at segment 6 and why it disagrees with the congruent registration position. `cmps_segment_plot` also returns a list, of which each element corresponds to one segment scale of this basis segment. Then for each segment scale, we will have two plots, `segment_plot` and `scale_ccf_plot`.

@@

@@

\begin{figure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot}segment\_plot for segment 6 at scale 1. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments.}
```{r segplot, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg.plot <- cmps_segment_plot(
  cmps_with_multi_scale, seg.idx = 6
  )
seg.plot[[1]]$segment_plot
```
\end{subfigure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot2}scale\_ccf\_plot shows the cross-correlation curve between the comparison signature and segment 6 at scale 1. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a candidate position for the consistent correlation peak; the blue dashed lines show the region of the tolerance zone. We can see here none of the five highest peaks agrees with the candidate position, so a consistent correlation peak cannot be identified and we don't take segment 6 as a congruent matching profile segment}
```{r segplot2, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
seg.plot[[1]]$scale_ccf_plot
```
\end{subfigure}
\caption{\label{fig:segplots}some text.}
\end{figure}

<!-- ```{r, echo=FALSE, eval=FALSE, out.width="300px", fig.cap="segment\\_plot for segment 6 at scale 1. The original position of segment 6 is indicated by the solid black line. Positions where the segment achieves the 5 highest cross-correlations are indicated by the dashed line segments. "} -->
<!-- knitr::include_graphics("img/segplot1.png", dpi = 100) -->
<!-- ``` -->

<!-- ```{r, echo=FALSE, out.width="300px", fig.cap="scale\\_ccf\\_plot shows the cross-correlation curve between the comparison signature and segment 6 at scale 1. The five highest peaks are marked by dots. The vertical red dashed line indicates the congruent registration position; the green dashed line shows a candidate position for the consistent correlation peak; the blue dashed lines show the region of the tolerance zone. We can see here none of the five highest peaks agrees with the candidate position, so a consistent correlation peak cannot be identified and we don't take segment 6 as a congruent matching profile segment"} -->
<!-- knitr::include_graphics("img/segplot2.png", dpi = 100) -->
<!-- ``` -->

@@

\begin{figure}
\begin{subfigure}[t]{\textwidth}
\caption{\label{fig:segplot3}put segment\_plot and scale\_ccf\_plot of all scales together. We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1). Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment. Here we can also see clearly that increasing segment length can reduce the number of false positive peaks.}
```{r segplot3, opts.label="codefig", echo=TRUE, out.width='\\textwidth', warning = FALSE}
library(ggpubr)

ggarrange(
  plotlist = 
    unlist(seg.plot, 
           recursive = FALSE),
  ncol = 2, 
  nrow = 3)
```
\end{subfigure}
\caption{\label{fig:seg_all} some text.}
\end{figure}

<!-- ```{r, echo=FALSE, out.width="400px", fig.cap="put segment\\_plot and scale\\_ccf\\_plot of all scales together. We are identifying five highest peaks at scale 1, three peaks at scale 2, and one peak at scale 3 since npeaks.set = c(5, 3, 1). Putting these plots together can help better understand why segment 6 is not a congruent matching profile segment. Here we can also see clearly that increasing segment length can reduce the number of false positive peaks."} -->
<!-- knitr::include_graphics("img/segplot3.png", dpi = 100) -->
<!-- ``` -->
